A Hitchhiker's Guide to Reproducible Research" # replace with something serious

### 2021-05-05 manuscript.Rmd
cite simsem and simstudy closes #37

Data simulation is particularly easy in lavaan syntax using the function `simulateData`. More complicated simulations (for example, including missing data simulation) are possible with other packages, e.g., simsem <!--AP please add reference, and possibly other packages-->. The following code simulates data from the population model `model_truth` with 1.000 cases in each group.

>>>>

Data simulation is particularly easy in lavaan syntax using the function `simulateData`. More complicated simulations (for example, including missing data simulation) are possible with other packages, e.g., simsem [@simsem], or simstudy [@goldfeldSimstudyIlluminatingResearch2020]. The following code simulates data from the population model `model_truth` with 1.000 cases in each group.
